---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(tidyverse)
library(polite)
library(rvest)
```

# Loading client data

```{r}
break_glass_in_case_of_emergency <- readRDS("./data-raw/break_glass_in_case_of_emergency.Rds")
cust_dev <- readRDS("./data-raw/cust_dev.Rds")
cust_sleep <- readRDS("./data-raw/cust_sleep.Rds")
customer <- readRDS("./data-raw/customer.Rds")
device <- readRDS("./data-raw/device.Rds")
```

# Getting external data

## Web scraping industry data

```{r}

```

# Census API

```{r}

```

