---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(tidyverse)
library(polite)
library(rvest)
library(sf)
library(geojsonsf)
```

# Loading client data

```{r}

```

# Getting external data

## Web scraping industry data

```{r}

```

# Census API

```{r}
# install.packages("cancensus")
library(cancensus)


options(cancensus.api_key = "CensusMapper_62d5b97e34abdba3579b1900089c724a",
        cancensus.cache_path = "cache") # this sets a folder for your cache


# get all regions as at the 2016 Census (2020 not up yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # Figure out what CSD means in Census data
  as_census_region_list()

# This can take a while
# We want to get household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD', geo_format = "sf")

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)

```

